---
title: "FB Template"
author: "Dr K"
date: "May 23, 2019"
output: html_document
---

```{r}
#Facebook Survey Template

Myurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vSOQJSNr-6RJoqPJOsyrB5g1R3V4oNJss4oBuuc0WLlYJBo-YxSbyE9MVpCLvcgzD7sdlDq6m6VXYo0/pub?gid=0&single=true&output=csv"

Facebook_Survey<-read.csv(url(Myurl))
Facebook_Survey
age<-Facebook_Survey$Age
gender<-Facebook_Survey$Gender
visits<-Facebook_Survey$VisitsPerWeek
friends<-Facebook_Survey$Friends
facebook<-Facebook_Survey$Facebook
#facebook
#age
#gender
#visits
#friends
#typeof(
#Facebook_Survey)
average_user_visits=sum(visits)/sum(facebook)
average_user_age=sum(age)/sum(facebook)
average_users=mean(facebook)
average_user_friends=sum(friends)/sum(facebook)

men<-length(gender)-sum(gender)
women<-sum(gender)
print("Number of people in survey")
men+women
print("Number of men in survey")
men
print("Number of women in survey")
women
print(" Average number of visits per week")
average_user_visits
print(" Average age of people in survey")
average_user_age
print(" Percent of people in survey who use Facebook")
average_users*100
print(" Average number of Facebook friends of Facebook users in survey")
average_user_friends
```
# Bar chart of Facebook users by sex


# number men in survey how do not have a Facebook account.

```{r}
nfm<-0
for (i in 1:length(gender)){
 if ( gender[i] ==0 & facebook[i]==0)
nfm=nfm+1}
print("number men in survey how do not have a Facebook account.")
nfm


# number men in survey how have a Facebook account.
fm<-0
for (i in 1:length(gender)){
 if ( gender[i] ==0 & facebook[i]==1)
fm=fm+1}
print("number men in survey how have a Facebook account.")
fm

# number women in survey how do not have a Facebook account.
nfw<-0
for (i in 1:length(gender)){
 if ( gender[i] ==1 & facebook[i]==0)
nfw=nfw+1}
print("number women in survey how do not have a Facebook account.")
nfw


# number women in survey how have a Facebook account.
fw<-0
for (i in 1:length(gender)){
 if ( gender[i] ==1 & facebook[i]==1)
fw=fw+1}
print("number women in survey how have a Facebook account.")
fw

# Create the matrix of the values.
values <- matrix(c(nfm,nfw,fm,fw), nrow = 2, ncol = 2, byrow= TRUE)
values

#Create the input vectors.
colors = c("green","orange")
sex <- c("Men","Women")
status <- c("No Facebook","Facebook")

# Create the bar chart
barplot(values, main = "Facebook user breakdown by sex", names.arg = sex, xlab = "Men vs Women", ylab = "number", col = colors)


# Add the legend to the chart
legend("topright", status, cex = .6, fill = colors)


#Facebook users who are men

# values to be removed
x<-c(0)
y<-c(1)

# positions where facebook has zeros or gender is 1
Positions= which(facebook %in% x | gender %in% y)
men_user_visits<- visits[-Positions]
men_user_visits
men_user_age<-age[-Positions]
men_user_friends<-friends[-Positions]
men_user_friends


#Facebook users who are women

# positions where Facebook has zeros or gender is 0
Positions= which(facebook %in% x | gender %in% x)
women_user_visits<- visits[-Positions]
women_user_visits
women_user_age<-age[-Positions]
women_user_friends<-friends[-Positions]


# Bar chart of  user ages by sex
#women age breakdown
z=seq(from=10, to=15,by=1)
p= which( women_user_age %in% z) 
women_user_10to15<-lengths(p)
women_user_10to15
z=seq(from=16, to=21,by=1)
p= which( women_user_age %in% z)
women_user_16to21<-lengths(p)
z=seq(from=22, to=27,by=1)
p= which( women_user_age %in% z)
women_user_22to27<-lengths(p)
z=seq(from=28, to=33,by=1)
p= which( women_user_age %in% z)
women_user_28to33<-lengths(p)
z=seq(from=34, to=39,by=1)
p= which( women_user_age %in% z)
women_user_34to39<-lengths(p)
z=seq(from=40, to=45,by=1)
p= which( women_user_age %in% z)
women_user_40to45<-lengths(p)
z=seq(from=46, to=51,by=1)
p= which( women_user_age %in% z)
women_user_46to51<-lengths(p)
z=seq(from=52, to=57,by=1)
p= which( women_user_age %in% z)
women_user_52to57<-lengths(p)
z=seq(from=58, to=63,by=1)
p= which( women_user_age %in% z)
women_user_58to63<-lengths(p)
z=seq(from=64, to=69,by=1)
p= which( women_user_age %in% z)
women_user_64to69<-lengths(p)
z=seq(from=70, to=75,by=1)
p= which( women_user_age %in% z)
women_user_70to75<-lengths(p)
z=seq(from=76, to=81,by=1)
p= which( women_user_age %in% z)
women_user_76to81<-lengths(p)
z=seq(from=82, to=87,by=1)
p= which( women_user_age %in% z)
women_user_82to87<-lengths(p)
z=seq(from=88, to=93,by=1)
p= which( women_user_age %in% z)
women_user_88to93<-lengths(p)
z=seq(from=94, to=98,by=1)
p= which( women_user_age %in% z)
women_user_94to99<-lengths(p)

#men age breakdown
z=seq(from=10, to=15,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_10to15<-0, men_user_10to15<-length(p))
men_user_10to15

z=seq(from=16, to=21,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_16to21<-0, men_user_16to21<-length(p))
men_user_16to21

z=seq(from=22, to=27,by=1)
p<- which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_22to27<-0, men_user_22to27<-length(p))
men_user_22to27

z=seq(from=28, to=33,by=1)
p<- which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_28to33<-0, men_user_28to33<-length(p))
men_user_28to33

z=seq(from=34, to=39,by=1)
p<- which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_34to39<-0, men_user_34to39<-length(p))
men_user_34to39

z=seq(from=40, to=45,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_40to45<-0, men_user_40to45<-length(p))
men_user_40to45

z=seq(from=46, to=51,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_46to51<-0, men_user_46to51<-length(p))
men_user_46to51

z=seq(from=52, to=57,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_52to57<-0, men_user_52to57<-length(p))
men_user_52to57

z=seq(from=58, to=63,by=1)
p<- which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_58to63<-0, men_user_58to63<-length(p))
men_user_58to63

z=seq(from=64, to=69,by=1)
p<- which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_64to69<-0, men_user_64to69<-length(p))
men_user_64to69

z=seq(from=70, to=75,by=1)
p<- which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_70to75<-0, men_user_70to75<-length(p))
men_user_70to75

z=seq(from=76, to=81,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_76to81<-0, men_user_76to81<-length(p))
men_user_76to81

z=seq(from=82, to=87,by=1)
p<- which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_82to87<-0, men_user_82to87<-length(p))
men_user_82to87

z=seq(from=88, to=93,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_88to93<-0, men_user_88to93<-length(p))
men_user_88to93

z=seq(from=94, to=98,by=1)
p<-which( men_user_age %in% z)
ifelse(identical(p,integer(0))==TRUE
, men_user_94to98<-0, men_user_94to98<-length(p))
men_user_94to98

men_user_age
```

# Create the matrix of the values.
values <- matrix(c(men_user_10to15,women_user_10to15,men_user_16to21,women_user_16to21, men_user_22to27,women_user_22to27, men_user_28to33,women_user_28to33, nrow = 2, ncol =4 , byrow= TRUE)
values


```{r}
# Create the matrix of the values.
values <- matrix(c(1,2,3,4,5,6,7,8), nrow = 2, ncol = 4, byrow= FALSE)
values

#Create the input vectors.
colors = c("green","orange")
Ages <- c("10-15","16-21","22-27","28-33")
status <- c("men","women")

# Create the bar chart
barplot(values, main = "Facebook user ages by sex", names.arg = Ages, xlab = "Men vs Women", ylab = "number", col = colors)

# Add the legend to the chart
legend("bottomright", status, cex = .8, fill = colors)

z=seq(from=10, to=15,by=1)
p= which( men_user_age %in% z)
#get rid of integer(0)
ifelse(identical(p,integer(0))==TRUE
, men_user_10to15<-0, men_user_10to15<-lengths(p))

```
#value = integer(0)
#identical(value, integer(0))
# [1] TRUE
#ifelse(identical(value, #integer(0))==TRUE,value<-0, print("failed"))


ifelse(test_expression, x, y)

identical(p,integer(0))


#First regression model: Scatter plot and regression line. Analyzing how well facebook visits predicts number of Facebook friends.

```{r}
# values to be removed
y<-c(0)
# positions where Facebook has zeros
Positions= which(facebook %in% y)
Positions
#Remove people from visits who do not have a Facebook page
user_visits=visits[-Positions]
user_visits
#Remove people from friends  who do not have a Facebook page
user_friends=friends[-Positions]
user_friends
#Remove people from visits who do not have a Facebook page
user_age=age[-Positions]
user_age


#Model 1: How well facebook visits predict number of Facebook friends

M1 <- lm(user_friends~user_visits, data=Facebook_Survey)
summary.lm(M1)
summary(M1)$adj.r.squared

plot(user_visits, user_friends, xlab="average number of visits per week", ylab="number of Facebook friends", main="How well facebook visits predicts number of Facebook friends")
#mean.visits<-mean(visits)
#abline(h=mean.visits)
abline(M1, col="red")

#Model 2: How well age predicts number of Facebook friends?

M2 <- lm(user_friends~user_age, data=Facebook_Survey)
summary.lm(M2)
summary(M2)$adj.r.squared

plot(user_age, user_friends, xlab="age", ylab="number of Facebook friends", main="How well age predicts number of Facebook friends")
#mean.visits<-mean(visits)
#abline(h=mean.visits)
abline(M2, col="red")


#Multiple regression model: Analyzing how well facebook visits and age predicts number of Facebook friends.

M12<- lm(user_friends~user_visits+user_age, data=Facebook_Survey)
summary.lm(M12)
summary(M12)$adj.r.squared

#Predict number of Facebook friends from user a age=28 with visits=20 

new <- data.frame(name=c("Ryan"),age=c(104), visits=c(98))

#Model 1 Prediction:
print("Model 1: predicted number of Facebook friends of a 28 year old user who visits the site 20 times per week")
predict.lm(M1,new)

#95% confidence interval for Model 1
predict.lm(M1,new,interval = "confidence",se.fit = TRUE)

#Model2 Prediction:
print("Model 2: predicted number of Facebook friends of a 28 year old user who visits the site 20 times per week")

predict.lm(M2,new)

#95% confidence interval for Model 2
predict.lm(M2,new,interval = "confidence",se.fit = TRUE)


# Model 3 Prediction:
print("Model 3: predicted number of Facebook friends of a 28 year old user who visits the site 20 times per week")

predict.lm(M12,new)
   
#95% confidence interval for Model 3:
predict.lm(M12,new,interval = "confidence",se.fit = TRUE)

#Fourth regression model: Scatter plot and regression line. Analyzing how well facebook visits predicts number of Facebook friends for men only.

M3 <- lm(men_user_friends~men_user_visits, data=Facebook_Survey)
summary.lm(M3)
summary(M3)$adj.r.squared

plot(men_user_visits, men_user_friends, xlab="average number of visits per week", ylab="number of Facebook friends", main="How well facebook visits predicts number of Facebook friends for men")
#mean.visits<-mean(visits)
#abline(h=mean.visits)
#abline(M3, col="red")
men_user_visits
men_user_friends
plot(7,20)



```